Neural Networks for Neural Tumors

### 2025-06-01 latex/draft.tex
minor adjustments

\author{
\IEEEauthorblockN{\large Joe Vogel}
\IEEEauthorblockA{\textit{UC Davis Computer Science} \\
jvogel@ucdavis.edu}

\and
\IEEEauthorblockN{\large Nam Nguyen}
\IEEEauthorblockA{\textit{UC Davis Computer Science} \\
ncnn@ucdavis.edu}

\and
\IEEEauthorblockN{\large Jonathan Mo}
\IEEEauthorblockA{\textit{UC Davis Computer Science} \\
jtnmo@ucdavis.edu}

\and
\IEEEauthorblockN{\large Aryan Karnwal}
\IEEEauthorblockA{\textit{UC Davis Computer Science} \\
akarnwal@ucdavis.edu}

\and
\IEEEauthorblockN{\large Richard Ho}
\IEEEauthorblockA{\textit{UC Davis Computer Science} \\
rdho@ucdavis.edu}
}

@@

The dataset used for this project comes from a group of brilliant students at Savitribai Phule Pune University in India. It can be found for free on Kaggle\textsuperscript{4}. It is a well respected and reviewed dataset. The data consists of 3264 files, which are all images of MRI scans. The images are divided into four sets. There are three different tumor sets, and one set of “no tumor” scans. Considering each image in our dataset is already classified, our model's training is supervised, as opposed to unsupervised, where each image would not have an associated classification to begin with.

>>>>

% old author block
% \author{
% \IEEEauthorblockN{\large Joe Vogel}
% \IEEEauthorblockA{\textit{UC Davis Computer Science} \\
% jvogel@ucdavis.edu}

% \and
% \IEEEauthorblockN{\large Nam Nguyen}
% \IEEEauthorblockA{\textit{UC Davis Computer Science} \\
% ncnn@ucdavis.edu}

% \and
% \IEEEauthorblockN{\large Jonathan Mo}
% \IEEEauthorblockA{\textit{UC Davis Computer Science} \\
% jtnmo@ucdavis.edu}

% \and
% \IEEEauthorblockN{\large Aryan Karnwal}
% \IEEEauthorblockA{\textit{UC Davis Computer Science} \\
% akarnwal@ucdavis.edu}

% \and
% \IEEEauthorblockN{\large Richard Ho}
% \IEEEauthorblockA{\textit{UC Davis Computer Science} \\
% rdho@ucdavis.edu}
% }

\author{
\centering
\begin{minipage}[t]{0.9\textwidth}
  \centering
  \begin{tabular}{ccc}
    Joe Vogel & Nam Nguyen & Jonathan Mo \\
    \textit{UC Davis Computer Science} & \textit{UC Davis Computer Science} & \textit{UC Davis Computer Science} \\
    jvogel@ucdavis.edu & ncnn@ucdavis.edu & jtnmo@ucdavis.edu \\
    \vspace{0.6em}
  \end{tabular}
  \begin{tabular}{cc}
    Aryan Karnwal & Richard Ho \\
    \textit{UC Davis Computer Science} & \textit{UC Davis Computer Science} \\
    akarnwal@ucdavis.edu & rdho@ucdavis.edu \\
  \end{tabular}
\end{minipage}
}

@@

The dataset used for this project comes from a group of brilliant students at Savitribai Phule Pune University in India. It can be found for free on Kaggle\textsuperscript{4}. It is a well respected and reviewed dataset. The data consists of 3264 files, which are all images of MRI scans. The images are divided into four sets. There are three different tumor types, and one set of “no tumor” scans. Considering each image in our dataset is already classified, our model's training is supervised, as opposed to unsupervised, where each image would not have an associated classification to begin with.
